### 2020-07-02 text/content.tex
Pull most recent version from OverLeaf

\section*{Introduction}
Social distancing measures are effective non-pharmaceutical interventions against the rapid spread of epidemics \cite{Bootsma2007-ww,Markel2007-ad,Hatchett2007-gc,Wilder-Smith2020-jj}. Many countries have implemented or are considering measures such as school closures, prohibition of large gatherings and restrictions on non-essential stores and transportation to slow down the spread of the 2019--20 coronavirus pandemic \cite{Anderson2020-qk,Cohen2020-jw,Thompson2020-lc,noauthor_2020-xi}. What are the economic effects of such social distancing interventions? Which businesses are most affected by the restrictions?

Past research has analyzed the efficacy of social distancing interventions on reducing the spread of epidemics using the 1918 Spanish Flu in the U.S. \cite{Hatchett2007-gc,Markel2007-ad,Bootsma2007-ww} and seasonal viral infections in France \cite{Adda2016-mn}. Our knowledge of economic impacts, however, is limited \cite{Wren-Lewis2020-vc}. For this question, past data may be less relevant, as the importance of face-to-face communication has increased steadily in the last 100 years through urbanization \cite{Henderson2010-mv,Henderson2002-ji} and specialization increased in business services as well \cite{Herrendorf2014-jx,Duarte2019-kc}.

The starting point of this paper is the observation that many sectors rely heavily on face-to-face communication in the production process \cite{Charlot2004-zr,Tian2019-wq}. We build a model of communication to understand how limiting face-to-face interaction increases production costs. Without social distancing, workers specialize in a narrow range of tasks and interact with other workers completing other tasks. This division of labor reduces production costs but requires frequent contact between workers. In the model, the number of contacts per worker is the most frequent in high-population-density areas in businesses where the division of labor is important. When face-to-face interaction is limited, these are exactly the businesses that suffer the most.

To measure business disruptions from social distancing, we turn to recent data on the task descriptions of each occupation \cite{National_Center_for_ONET_Development2020-wj} and the precise geographic location of non-farm businesses in the U.S. \cite{CBP}. We construct three groups of occupations and study their distribution in space. First, some occupations require face-to-face communication several times a week with other workers. Examples of these \emph{teamwork-intensive} occupations include maintenance, personal care related occupations and health care professionals. Other occupations require frequent contact with customers. Counselors, social workers and salespersons are examples of such \emph{customer-facing} occupations. The third group of workers may need to be in physical proximity of one another even if they do not communicate, for example, to operate machinery or access key resources. Examples of such occupations requiring \emph{physical presence} are drivers and machine operators, especially in mining and water transport, where crammed working environments are common.

The spatial distribution of employment matters because face-to-face interactions are more frequent in dense cities \cite{Charlot2004-zr,Tian2019-wq}. So any social distancing intervention imposes disproportionately more limitation on urban sectors. We use our theory-motivated measures to estimate which sectors and which locations will be particularly hurt by social distancing.

@@

Fig \ref{fig1} illustrates the division of labor between workers. Horizontal movement represents production along a range of tasks ($Z=1/n$), vertical movement represents interaction ($\tau$). We note three potential interpretations of our model. First, when workers work in teams, they can efficiently divide labor among themselves (panel A). The benefit of a larger team is better specialization. Second, communication may involve the customer (panel B). The benefit of more frequent interaction with the customer is a product or service that is better suited to their needs. Third, workers may need access to a key physical resource, such as a machine, vehicle or an oil well (panel C). In this case, even if they do not communicate, they may be subject to social distancing measures. The key assumption behind all three interpretations is that frequent interaction increases productivity, whether happening between workers, between workers and customers, or between workers and machines.

@@

\subsection*{The cost of communication}
Businesses may differ in $\chi$, how important communication is in their production process. Another source of heterogeneity is the cost of communication between workers, which we specify further as follows.

When workers meet face to face, communication costs depend inversely on the population density in the neighborhood of the firm, $\tau=d^{-\varepsilon}$ with $\varepsilon>0$. This captures the Marshallian externality of knowledge spillovers \cite{Marshall1920-ps}, which happen more easily in densely populated areas \cite{Charlot2004-zr,Rossi-Hansberg2007-tm,Ioannides2008-bs,Tian2019-wq}. Contacts will be more frequent in dense areas,
\begin{equation}\label{communication}
	n^*(d) = d^{\varepsilon(1-\chi)}.
\end{equation}
The unit cost of production is
\begin{equation}\label{cost2}
c(d) = d^{-\varepsilon\chi}/\chi.
\end{equation}
Firms in dense areas face lower unit costs \cite{Ciccone1996-gu}, but this agglomeration benefit may be offset by higher wages and land rents in places with high population density \cite{Eberts1982-zf,Madden1985-pq,Combes2019-ud}. In spatial equilibrium (not modeled here), firms with high communication needs will choose to locate in high-density areas \cite{Tian2019-wq}.

\subsection*{Social distancing measures}
We study the effect of a social distancing intervention that puts an upper limit $N$ on the number of face-to-face contacts. Firms can mitigate the disruption from this measure by moving communication online, but this is more costly per contact than face-to-face communication.

The optimal number of contacts without social distancing is given by Eq \eqref{communication}. Firms with $n^*>N$ are limited by social distancing. Without moving communication online, their unit cost will increase to $c' = N d^{-\varepsilon} + N^{-\gamma}/\gamma$, which is greater than the optimal cost,
\begin{equation}\label{socdist}
\frac{c'(d)}{c(d)} 
	= \chi \frac{N}{n^*(d)} + (1-\chi) \left(\frac{N}{n^*(d)}\right)^{-\gamma}>1.
\end{equation}
The first term of the weighted average is less than one, representing a reduction in communication costs once the number of contacts is limited. The second term is greater than one due to the fact that every worker has to complete a wider range of tasks than before, and they lose the benefit of specialization. Because $n^*$ is the cost-minimizing communication choice of the firm, the second term dominates, and production costs increase with social distancing.

If the firm chooses to use telecommunication, the cost per contact will be $T>d^{\varepsilon}$ (otherwise the firm would have used telecommunication before). The proportional increase in production costs in this case is given by
\begin{equation}\label{telco}
\frac{c''(d)}{c(d)} 
	= T^\chi d^{\varepsilon \chi}
	>1.
\end{equation}
In both cases, the cost increase is highest for communication-intensive firms (large $\gamma$ and $\chi$) and those operating in a high-density area (high $d$ and hence high $n^*$).

Fig \ref{fig2} displays the ratio of production costs under social distancing to the optimal production costs as a function of density. Firms in low-density areas are unaffected by social distancing since they do not have many contacts anyway. Those in intermediate-density areas would suffer less of a cost increase by switching to telecommunication. Firms in the highest-density areas will stick to face-to-face communication, which is still the more efficient form of communication despite restrictions. However, they will suffer the greatest cost increase.

\begin{figure}[!h]
\plos{\centering\input{fig2-input}}

\caption{{\bf Both social distancing and telecommunication hurt firms in dense areas more.}
See Eq \eqref{socdist} and Eq \eqref{telco} for the relative production costs under the two interventions.}
\label{fig2}
\end{figure}

\section*{Data and methodology}
To estimate the potential disruptions from social distancing, we need a measure of the importance of worker interaction (corresponding to $\chi$ in the model) and its cost (captured by population density $d$).

@@

Social distancing interventions limit the interaction between people and regulate physical proximity between individuals. We thus focus on three related job characteristics based on work context and work activity described in O*NET. The first two indicators capture how communication-intensive the job is. Communication can be of two types: internal communication with co-workers (\emph{teamwork}) or external communication directly with customers (\emph{customer-facing}). The third indicator takes into consideration the possibility that workers may need to be in physical proximity of one another even if they do not communicate. We create an index that shows how important \emph{physical presence} is to perform a given job. Table \ref{table1} details the specific O*NET indexes that contribute to each of our three measures.
As social distancing measures only limit personal communication, for communication indexes, we require that the necessary face-to-face communication happens at least several times a week. 
In teamwork, face-to-face meetings can often be substituted by more structured communication, for which working from home is not as disruptive. To allow for this possibility, we only classify occupations as teamwork-intensive where both emails and letters and memos are less frequent forms of communication than face-to-face meetings. This excludes most managers and certain business services. Similarly, for physical presence, we require at least a certain degree of proximity to other workers which corresponds to working in a shared office.

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Definition of social distancing indexes.}}
\begin{tabular}{|l|l|l|}
\hline
{\bf Index} & {\bf Tasks} & {\bf Context} 
\\ \thickhline
\hline
Teamwork & Work With Work Group or Team & Face-to-face  \\
& Provide Consultation and Advice to Others & discussions  \\
& Coordinating the Work and Activities of Others & several times a week \\
& Guiding Directing and Motivating Subordinates & \& more often than \\
& Developing and Building Teams & emails, letters, memos\\
\hline
Customer & Deal With External Customers & Face-to-face\\
&  Performing for or Working Directly with the Public & discussions \\
& Assisting and Caring for Others & several \\
& Provide Consultation and Advice to Others & times a week\\
& Establishing and Maintaining Interpersonal Relationships &\\
\hline
Presence & Handling and Moving Objects & Density of \\
& Operating Vehicles, Mechanized Devices or Equipment & co-workers \\
& Repairing and Maintaining Electronic Equipment &  like shared\\
& Repairing and Maintaining Mechanical Equipment & office or more\\
& Inspecting Equipment, Structures, or Material &\\
\hline
\hline
\end{tabular}
\begin{flushleft} Each social distancing index (column 1) is created as an arithmetic average of the component indexes (column 2). To be classified an affected occupation, the average has to exceed 62.5 and the work context index has to exceed the threshold in column 3.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{table}

@@

As a next step, we calculate for each sector the share of workers whose job requires a high level of teamwork, customer contact and physical presence. 
We use the same sectoral breakdown as the Current Employment Statistics (CES) \cite{CES}. As all the indexes are an absolute value running from 0 to 100, we use 62.5 as a cutoff to define a job to be teamwork-intensive, customers contact-intensive or job that require physical presence from the worker.  The occupation structure of the industries are retrieved from the official industry-occupation matrix \cite{employment-matrix}, we use the employment statistics by occupation-industry for February 2020.

@@

To measure the heterogeneity in the cost of communication, we measure population density in the neighborhood of businesses. The assumption in the model is that communication costs are lower in dense areas. This is consistent with the fact that communication-intensive sectors such as business services and advertising, together with central administrative offices of production firms tend to be concentrated in high-density areas \cite{Aarland2007-dh}.

The location of sectors comes from the County Business Patterns (CBP) data for 2017 \cite{CBP}. For a finer spatial resolution, we use the data tabulated by ZIP-Code Tabulation Areas. The CBP lists the number of establishments of a certain size for each ZIP-code and NAICS industry code. Because establishment sizes are given in bins (e.g., 1--4 employees), we take the midpoint of each bin as our estimated employment (e.g., 2.5 employees). In small industries and ZIP codes, the Census omits some size categories to protect the confidentiality of businesses. We impute employment in these plants from the national size distribution of plants in the same NAICS industry. Our estimated industry-level employment is a very good approximation to official employment statistics \cite{CES}. The correlation between our estimates based on CBP and the employment reported in CES is 0.98.

To understand the heterogeneity across regions, we average the share of workers in teamwork-intensive, customer-facing and physical presence occupations across industries active in each ZIP code. For each of the three occupation groups, let $\xi_{og}$ denote the indicator whether occupation $o$ belongs to group $g$. The industry share of workers in the occupation group is given by $\sum_o s_{io}\xi_{og}$. We compute the regional share of the occupation group as an employment-weighted average across industries, $\sum_i l_{ir}\sum_o s_{io}\xi_{og}/\sum_i l_{ir}$, where $l_{ir}$ is the estimated employment of industry $i$ in region (ZIP code) $r$. Because we only have industry but not occupation data by location, we have assumed that the occupation distribution within the sector, $s_{io}$, does not vary across locations. The fact that the CBP tabulates employment by establishments rather than firms makes this a good approximation. For example, a sporting good producer may also have an administrative office and a retail store in different locations, but these will be classified in their respective NAICS sectors rather than in sporting good manufacturing.

We use population density to measure how locations differ in the costs of communication. We also experimented with using employment densities instead of population densities. Results were very similar, as the two measures are highly correlated with the exception of very high employment-density urban centers where population is more sparse \cite{Heblich2017-lb}.

\subsection*{Counterfactual calculations}
To gauge the magnitude of the effect of social distancing, we calibrate the parameters of the model and compute the effect of a policy that limits the number of worker contacts. At the same time, we let the government introduce a proportional wage subsidy $\lambda$ to help offset the costs from lower interaction. With this subsidy, the cost of labor will be $(1-\lambda)$. We ask what level of $\lambda$ would compensate businesses for the communication disruption caused by social distancing. Using the cost change in Eq \ref{socdist}, we can express
\begin{equation}\label{subsidy}
    \lambda_{ir} = 1 -
        \frac{1-\chi_i}{1-\chi_i N/n_{ir}^*}
        \left(
        \frac{N}{n_{ir}^*}
        \right)^{\gamma_i}>0.
\end{equation}
The compensating wage subsidy increases in the importance of communication $\chi_i$ and the optimal number of contacts $n^*_{ir}$, and decreases in the number of allowed contacts $N$. The subscripts note that communication share is industry specific and the optimal number of contacts is both industry and region specific.

We calibrate the upper limit on personal contacts $N$ such that the overall number of contacts in the economy, when averaged across ZIP codes and industries, is reduced by half, $\sum_{i,r}l_{ir}\min\{N,n_{ir}^*\} = 0.5\sum_{i,r}l_{ir}n_{ir}^*$. Due to the inherent nonlinearity of the model, other interventions will have different effects.

To calibrate the importance of communication $\chi_i$, note that it is the cost share of communication, and can be correspondingly calibrated to the employment share of communication-intensive occupations in industry $i$. Here we take all occupations that are either teamwork intensive or customer facing.

Population density in region $r$ can be measured directly in the data, as explained above.
The only remaining parameter to calibrate is the elasticity of the communication externality $\varepsilon$. We rely on previous estimates of agglomeration effects that capture the elasticity of total factor productivity with respect to population density \cite{Ciccone1996-gu}. In our model, the elasticity of unit costs (which can be construed as the inverse of productivity) with respect to density is $-\varepsilon\chi$ (Eq \eqref{cost2}). We calibrate $\varepsilon=0.02$ so that, across all ZIP codes and industries, a regression of log model-implied productivity ($\varepsilon\chi_i\ln d_r$) on log population density $\ln d_r$ yields an elasticity of 0.04 \cite[page 60]{Ciccone1996-gu}.

Given these parameter values, we compute the compensating wage subsidy for each industry in each ZIP code using Eq \ref{subsidy}. We report employment-weighted averages of this across sectors and across locations.

\section*{Results}
Table \ref{table2} displays the top five and the bottom five industries by 2-digit NAICS industries as sorted by the percentage of workers in communication-intensive occupations, excluding hospitals and clinics. Across industries, retail trade, accommodation and food services, arts, entertainment, and recreation, other services and educational services have the highest share of communication-intensive workers, exceeding 35 percent. Transportation, production, construction and agricultural industries are less reliant on face-to-face communication. This heterogeneity across industries is important to understand the effect of social distancing measures.

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Retail, professional services, finance and restaurants are the most communication intensive.}}
\begin{tabular}{|l|c|c|c|c|}
\hline
 & \multicolumn{3}{c}{\bf Communication} &  
\\ 
{\bf Industry} & {\bf Teamw.} & {\bf Custom.} & {\bf Overall} & {\bf Presence} 
\\ \thickhline
Retail trade &13&67&68&5\\
Accommodation \& food services &8&50&51&1\\
Arts, Entertainment, and Recreation &12&40&42&2\\
Other Services (except Public Admin.) &12&38&41&12\\
Educational Services &15&35&37&1\\
...&&&&\\
Wholesale Trade &8&16&20&12\\
Transportation and Warehousing  &8&10&16&32\\
Manufacturing &7&6&11&10\\
Construction &15&5&18&28\\
Agri., forestry, fishing \& hunting &4&4&7&23\\
 \thickhline

@@

Fig \ref{fig4} plots the share of workers in the three affected occupation groups across ZIP codes by population density. Customer-facing occupations are overrepresented in dense areas. In the highest population density ZIP codes, 43 percent of workers are employed in customer-facing occupations. Teamwork-intensive occupations are broadly distributed in space.

\begin{figure}[!h]
\plos{\includegraphics[width=0.7\linewidth]{fig4.pdf}}

\caption{{\bf Urban areas employ more workers in customer-facing occupations, less in occupations requiring physical presence.}
Locally weighted polynomial regression of average share of teamwork-intensive occupations, customer-facing occupations and occupations requiring physical presence across sectors within the ZIP code (bandwidth $=0.5$).}
\label{fig4}
\end{figure}

In the calibrated model, a social distancing policy that puts a cap on interactions per worker such that the total number of interactions drops by half nationwide is compensated a 12.2 percent wage subsidy. The distribution of the compensating wage subsidy is, however, unequal over space and across industries. 
New York City, with a population density about 20 times the average U.S. city, would require a 13.3 percent wage subsidy. 
By contrast, the compensating wage subsidy in agriculture, transportation and manufacturing would be less than 6 percent (Table \ref{table3}).

>>>>

\section*{Introduction}

Social distancing measures are effective non-pharmaceutical interventions against the rapid spread of epidemics \cite{Bootsma2007-ww,Markel2007-ad,Hatchett2007-gc,Wilder-Smith2020-jj}. Many countries have implemented measures such as school closures, prohibition of large gatherings and restrictions on non-essential stores and transportation to slow down the spread of the 2019--20 coronavirus pandemic \cite{Anderson2020-qk,Cohen2020-jw,Thompson2020-lc,noauthor_2020-xi}. What are the economic effects of such social distancing interventions? Which businesses are most affected by the restrictions?

Past research has analyzed the efficacy of social distancing interventions on reducing the spread of epidemics using the 1918 Spanish Flu in the U.S. \cite{Hatchett2007-gc,Markel2007-ad,Bootsma2007-ww} and seasonal viral infections in France \cite{Adda2016-mn}. Our knowledge of economic impacts, however, is limited \cite{Wren-Lewis2020-vc}. For this question, past data may be less relevant, as the importance of face-to-face communication has increased steadily in the last 100 years through urbanization \cite{Henderson2010-mv,Henderson2002-ji} and specialization increased in business services as well \cite{Herrendorf2014-jx,Duarte2019-kc}. 
Even if advances in information and communication technology made it increasingly possible to communicate with co-workers and customers without the need for physical face-to-face interactions, personal contacts are still inevitable in some industries. During the 2020 lockdown in the Netherlands only 31 percent of workers in the retail sector, 27 percent of the workers in the catering sector and 31 percent of the workers in the construction sector reported working from home \cite{von2020labour}.

The starting point of this paper is the observation that many sectors rely heavily on face-to-face communication in the production process \cite{Charlot2004-zr,Tian2019-wq}. We build a model of communication to understand how limiting face-to-face interaction increases production costs. Without social distancing, workers specialize in a narrow range of tasks and interact with other workers completing other tasks. This division of labor reduces production costs but requires frequent contact between workers. In the model, the number of contacts per worker is the most frequent in businesses where the division of labor is important. When face-to-face interaction is limited, these are exactly the businesses that suffer the most.

To measure business disruptions from social distancing, we turn to recent data on the task descriptions of each occupation \cite{National_Center_for_ONET_Development2020-wj}, the precise geographic location of non-farm businesses in the U.S. \cite{CBP}, and customer mobility patterns \cite{SafeGraph2020-gn}. We construct three groups of occupations. First, some occupations require face-to-face communication several times a week with other workers. Examples of these \emph{teamwork-intensive} occupations include maintenance, personal care related occupations and health care professionals. Other occupations require frequent face-to-face contact with customers. Retail salespersons, social workers and waiters and waitresses are examples of such \emph{customer-facing} occupations. The third group of workers may need to be in physical proximity of one another even if they do not communicate, for example, to operate machinery or access key resources. Examples of such occupations requiring \emph{physical presence} are drivers and machine operators, especially in mining and water transport, where crammed working environments are common. With our occupation level measures, we aim to capture the jobs that can be performed less efficiently from home. As O*NET measures the type of activities that are performed by the worker during normal times, we validate our indexes by using the American Time Use Survey (ATUS) \cite{ATUS}. The survey directly asks about the possibility of working from home.

To study how the patterns of interaction have changed in the U.S. during the Covid-19 pandemic, we use customer mobility data from SafeGraph \cite{SafeGraph2020-gn}. This dataset measures the number of visits to a business in a given month, as captured from several cell phone apps and made available to researchers in an anonymized form. ???????

@@

Fig \ref{fig1} illustrates the division of labor between workers. Horizontal movement represents production along a range of tasks ($Z=1/n$), vertical movement represents interaction ($\tau$). We note three potential interpretations of our model. First, when workers work in teams, they can efficiently divide labor among themselves (panel A). The benefit of a larger team is better specialization. Law firms, management teams, and IT service firms are prime examples of businesses where intensive communication leads to narrow specialization \cite{Garicano2009-jv}. Second, communication may involve the customer (panel B). The benefit of more frequent interaction with the customer is a product or service that is better suited to their needs. Restaurants, beauty salons, personal and social services require such frequent interaction exactly because their service is so customized. Third, workers may need access to a key physical resource (panel C). In this case, even if they do not communicate, they may be subject to social distancing measures. For example, operators of machines, vehicle drivers or workers on an oil rig are all very much tied to a key resource to do their job. The key assumption behind all three interpretations is that frequent interaction increases productivity, whether happening between workers, between workers and customers, or between workers and machines.

@@

\subsection*{Social distancing}

We study the effect of social distancing, which reduces the number of face-to-face contacts to some exogenous value $N$. This may be mandated by government orders to close certain places of business or stay at home. But it can also be the result of voluntary social distancing in response to the risk of infection.

The optimal number of contacts without social distancing is given by Eq \eqref{nstar}. Firms with $n^*>N$ are limited by social distancing. Without moving communication online, their unit cost will increase to $c' = N \tau + N^{-\gamma}/\gamma$, which is greater than the optimal cost,
\begin{equation}\label{socdist}
\frac{c'}{c} 
	= \chi \frac{N}{n^*} + (1-\chi) \left(\frac{N}{n^*}\right)^{-\gamma}>1.
\end{equation}
The first term of the weighted average is less than one, representing a reduction in communication costs once the number of contacts declines. The second term is greater than one due to the fact that every worker has to complete a wider range of tasks than before, and they lose the benefit of specialization. Because $n^*$ is the cost-minimizing communication choice of the firm, the second term dominates, and production costs increase with social distancing.

\section*{Data and methodology}
To estimate the potential disruptions from social distancing, we need a measure of the importance of worker interaction (corresponding to $\chi$ in the model) and its change (captured by the ratio $N/n^*$).

@@

Social distancing interventions limit the interaction between people and regulate physical proximity between individuals. We thus focus on three related job characteristics based on work context and work activity described in O*NET. The first two indicators capture how communication-intensive the job is. Communication can be of two types: internal communication with co-workers (\emph{teamwork}) or external communication directly with customers (\emph{customer-facing}). The third indicator takes into consideration the possibility that workers may need to be in physical proximity of one another even if they do not communicate. We create an index that shows how important \emph{physical presence} is to perform a given job. Table \ref{table1} details the specific O*NET indexes that contribute to each of our three measures.
As social distancing measures only limit personal communication, for communication indexes, we require that the necessary face-to-face communication happens at least several times a week. Face-to-face meetings can often be substituted by more structured communication, for which working from home is not as disruptive. To allow for this possibility, we only classify occupations as teamwork-intensive or customer-facing where both emails and letters and memos are less frequent forms of communication than face-to-face meetings. This excludes most managers and certain business services. Similarly, for physical presence, we require at least a certain degree of proximity to other workers which corresponds to working in a shared office.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Definition of social distancing indexes.}}
\begin{tabular}{|l+l|l|}
\hline
{\bf Index} & {\bf Tasks} & {\bf Context} 
\\ \thickhline
\hline
Teamwork & Work With Work Group or Team & Face-to-face  \\
& Provide Consultation and Advice to Others & discussions  \\
& Coordinating the Work and Activities of Others & several times a week \\
& Guiding Directing and Motivating Subordinates & \& more often than \\
& Developing and Building Teams & emails, letters, memos\\
\hline
Customer & Deal With External Customers & Face-to-face\\
&  Performing for or Working Directly with the Public & discussions \\
& Assisting and Caring for Others & several times a week \\
& Provide Consultation and Advice to Others & \& more often than\\
& Establishing and Maintaining Interpersonal Relationships & emails, letters, memos \\
\hline
Presence & Handling and Moving Objects & Density of \\
& Operating Vehicles, Mechanized Devices or Equipment & co-workers \\
& Repairing and Maintaining Electronic Equipment &  like shared\\
& Repairing and Maintaining Mechanical Equipment & office or more\\
& Inspecting Equipment, Structures, or Material &\\
\hline
\hline
\end{tabular}
\begin{flushleft} Each social distancing index (column 1) is created as an arithmetic average of the component indexes (column 2). To be classified an affected occupation, the average has to exceed 62.5 and the work context index has to exceed the threshold in column 3.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

With our occupation-level measures, we aim to capture the type of activities that require frequent face-to-face contact. Our assumption is that these activities cannot be effectively done from home. To validate this assumption, we use data from the American Time Use Survey (ATUS) \cite{ATUS}, which directly asks the workers whether they \emph{can} work from home. Fig. \ref{customer_validation} plots our customer-intensity measure, for each occupation, against the share of workers who reported in ATUS that they can work from home (dark filled circles). Indeed, most customer-facing occupations have very few workers who can work from home. The pattern is different if we look at occupations that rely more on email, letters, and memos for customer communication (light hollow circles). The majority of these workers can work from home. Interestingly, for each degree of working from home (horizontal axis), there is sufficient variation in the importance of customer contact (vertical axis). The same patterns can be observed for teamwork-intensive occupations (Fig. \ref{teamwork_validation}). This makes use conclude that dropping occupations primarily relying on email, letters and memos is sufficient to control for the potential to work from home.

\begin{figure}[!h]
\plos{\includegraphics[width=0.7\linewidth]{customer_atus_validation.pdf}}

\caption{{\bf Workers in customer-facing occupations with face-to-face interaction can rarely work from home.}
Filled circles represent the occupations where face-to-face contacts are more important than emails and memos. Hollow circles represent the occupations where emails and memos are more important than face-to-face contacts. The indexes are constructed as explained in main text. }
\label{customer_validation}
\end{figure}

\begin{figure}[!h]
\plos{\includegraphics[width=0.7\linewidth]{teamwork_atus_validation.pdf}}

\caption{{\bf Workers in teamwork-intensive occupations with face-to-face interaction can rarely work from home.}
Filled circles represent the occupations where face-to-face contacts are more important than emails and memos. Hollow circles represent the occupations where emails and memos are more important than face-to-face contacts. The indexes are constructed as explained in main text. }
\label{teamwork_validation}
\end{figure}

With our validated occupation measures in hand, our next step is to calculate for each sector the share of workers whose job requires a high level of teamwork, customer contact, and physical presence. 
We use the same sectoral breakdown as the Current Employment Statistics (CES) \cite{CES}. As all the indexes are an absolute value running from 0 to 100, we use 62.5 as a cutoff to define a job to be teamwork-intensive, customers contact-intensive, or job that requires physical presence from the worker.  The occupation structure of the industries are retrieved from the official industry-occupation matrix \cite{employment-matrix}, we use the employment statistics by occupation-industry for February 2020.

@@

To measure how the number of interactions has changed due to social distancing, we use data from SafeGraph \cite{SafeGraph2020-gn}, a data company that aggregates anonymized location data from numerous applications to provide insights about physical places. To enhance privacy, SafeGraph excludes census block group information if fewer than five devices visited an establishment in a month from a given census block group.

We use the Monthly Patterns file that captures the number of visits by mobile devices in the sample to more than 4 million points of interest (POIs) in each month. Each POI is assigned a specific address, including a ZIP code, and a 6-digit NAICS code. Because the pandemic hit different regions of the U.S. at different times, we use both the industry and the regional variation of customer mobility data. We aggregate monthly visits by 3-digit NAICS code and ZIP code. This enables us to measure by how much, for example, visits to clothing stores have declined in downtown Manhattan.

We measure the percentage change in the number of visits between February and May 2020. When the industry-ZIP cell received fewer than ten visits in either month or when visits data are missing in SafeGraph, we replace the change in visits with the average of the ZIP code.

To validate the customer mobility data, we check the location of sectors in the County Business Patterns (CBP) data for 2017 \cite{CBP}. For a finer spatial resolution, we use the data tabulated by ZIP-Code Tabulation Areas. The CBP lists the number of establishments of a certain size for each ZIP-code and NAICS industry code. We estimate the employment of each industry in each ZIP code to be able to compute employment-weighted national averages of our statistics of interest.

Because establishment sizes are given in bins (e.g., 1--4 employees), we take the midpoint of each bin as our estimated employment (e.g., 2.5 employees). In small industries and ZIP codes, the Census omits some size categories to protect the confidentiality of businesses. We impute employment in these plants from the national size distribution of plants in the same NAICS industry. Our estimated industry-level employment is a very good approximation to official employment statistics \cite{CES}. The correlation between our estimates based on CBP and the employment reported in CES is 0.98.

\subsection*{Counterfactual calculations}
To gauge the magnitude of the effect of social distancing, we compute the effect of the decline in the number of customer-worker contacts. At the same time, we let the government introduce a proportional wage subsidy $\lambda$ to help offset the costs from lower interaction. With this subsidy, the cost of labor will be $(1-\lambda)$.

We ask what level of $\lambda$ would exactly compensate businesses for the communication disruption caused by social distancing. When interactions decrease, $N<n^*$, production costs increase. We compute the subsidy $\lambda$, which, when given to every worker, would exactly offset the cost increase. This way the business would not have to fire any of its workers. The goal of this exercise is not to evaluate any particular employment support policy, but to get a sense of the magnitude of business disruptions.

Using the cost change in Eq \ref{socdist}, we can express the compensating labor subsidy of industry $i$ in region $r$ as
\begin{equation}\label{subsidy}
    \lambda_{ir} = 1 -
        \frac{1-\chi_i}{1-\chi_i N_{ir}/n_{ir}^*}
        \left(
        \frac{N_{ir}}{n_{ir}^*}
        \right)^{\gamma_i}>0.
\end{equation}
We calibrate $n_{ir}^*$ to match the number of customer visits to establishments of industry $i$ in ZIP-code $r$ in February 2020, assuming that these visits were optimal before the pandemic hit the U.S. The new number of visits, $N_{it}$ will be calibrated to the number of customer visits in May 2020. The compensating wage subsidy increases in the importance of communication $\chi_i$ and decreases in the change in cotacts $N_{ir}/n^*_{ir}$. The subscripts note that communication share is industry specific and the change in contacts is both industry and region specific.

To calibrate the importance of communication $\chi_i$, note that it is the cost share of communication, and can be correspondingly calibrated to the employment share of communication-intensive occupations in industry $i$. We then compute the compensating wage subsidy for each industry in each ZIP code using Eq \ref{subsidy}. We report employment-weighted averages of this across sectors and across locations.

\section*{Results}
Table \ref{table2} displays the top five and the bottom five industries by 2-digit NAICS industries as sorted by the percentage of workers in communication-intensive occupations, excluding hospitals and clinics. Across industries, retail trade, accommodation and food services, arts, entertainment, and recreation, other services and administrative and support and waste management and remediation services have the highest share of communication-intensive workers, exceeding 35 percent. Information, transportation, production, professional, scientific, and technical Services and agricultural industries are less reliant on face-to-face communication. This heterogeneity across industries is important to understand the effect of social distancing measures.

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Retail, accommodation and restaurants are the most communication intensive.}}
\begin{tabular}{|l+c|c|c+c|}
\hline
 & \multicolumn{3}{c}{\bf Communication} &  
\\ 
{\bf Industry} & {\bf Teamw.} & {\bf Custom.} & {\bf Overall} & {\bf Presence} 
\\ \thickhline
Retail trade &13&65&66&4\\
Accommodation \& food services &9&49&51&1\\
Arts, Entertainment, and Recreation &12&37&40&2\\
Other Services (except Public Admin.) &12&28&30&13\\
Admin. \& Support \& Waste Manag.  &	17&	24&	7&	27\\
\& Remed. Serv. &&&& \\
...&&&&\\
Information&	6&	13&	15&	9\\
Transportation and Warehousing&	8&	8&	14&	33\\
Prof., Scient., and Technical Serv.&	5&	10&	12&	1\\
Manufacturing&	7&	5&	9&	10\\
Agri., forestry, fishing \& hunting &	4&	1&	4&	23\\

 \thickhline

@@

Table \ref{table4} reports the results of regressing the log change in industry employment between February and May 2020 on our social distancing indexes. Each regression is estimated with unweighted ordinary least squares. Across the entire non-farm economy, employment has dropped by 13 percent (not seasonally adjusted) \cite{CES}.

As Column 1 shows, the drop was larger in industries with a larger share of customer-facing workers. There is no significant correlation between the share of workers with teamwork-intensive jobs or the share of workers requiring physical presence to do their work and employment losses. In Column 2, we control for the change in log customer visits. Indeed, changes in customer visits are positively correlated with changes in employment (both dropping for most of our industries). In Column 3, we introduce interactions with the change in log customer visits (as a proxy for $\ln (N/n^*)$) and the share of communication workers (as a proxy for $\chi$). As predicted by the model, the drop in customer visits has the largest effect on sectoral employment in sectors where the share of customer-facing workers is highest.

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Employment decline was sharpest in customer-facing industries.}}
\input{regression.tex}
\begin{flushleft} Regression results of change in log industry employment between February and May 2020 estimated by ordinary least squares (unweighted). Explanatory variables in Column 1 are the shares of customer-facing, teamwork-intensive and presence-requiring workers. Column 2 controls for the change in log monthly visits to industry establishments. Column 3 interacts the change in visits with the share of face-to-face intensive  workers in the two occupation groups. Robust standard errors are reported in parentheses. $p$-values are denoted by asterisk: * $<.1$ ** $<.05$ *** $<.01$.
Sample excludes hospitals, clinics, and government establishments, as well as farming and fishing which are not present in CBP.
\end{flushleft}
\label{table4}
%\end{adjustwidth}
\end{table}

As we see from the regression results above, the largest decline in sectoral employment are in sectors where the share of customer-facing workers is highest. We hence use the share of customer-facing workers for the following analysis.

In the calibrated model, the social distancing that took place between February and May 2020 would be compensated by a 39.9 percent wage subsidy. The distribution of the compensating wage subsidy is, however, unequal across industries. Retail trade, where customer visits practically ground to a halt, would require a 234 percent wage subsidy. By contrast, the compensating wage subsidy in agriculture, transportation and manufacturing would be less than 2 percent (Table \ref{table3}).
